Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2021-11-10 proposalPres.tex
Added two figures into /figs/img folder
Updated labNotebook.tex with 11/9 entry

Updated proposalPres.tex with Acceleration System Model Estimation Results

@@

\begin{frame}{Simulation Results}
  \begin{block}{}
 \begin{itemize}
	\item Best fit percentage of the by-wire steering estimated model is 85.54
	\item Best fit percentage of the manual steering estimated model is 90.27
 \end{itemize}
 \begin{figure}
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
        \caption{Output of Estimated By-Wire System Model}
        \label{fig:byWireSteerModel}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
        \caption{Output of Estimated Manual System Model}
        \label{fig:manualSteerModel}
    \end{minipage}
\end{figure}
  \end{block}
\end{frame}

>>>>

\begin{frame}
\begin{figure}[h]
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=4in]{figs/inkscape/steeringModelBlockDiagram}
    \caption{Steering System Block Diagram}
    \label{fig:steerBlockDiag}
\end{figure}
\end{frame}

@@

\begin{frame}{Simulation Results}
  \begin{block}{Steering System}
 \begin{itemize}
	\item Best fit percentage of the by-wire steering estimated model is 85.54
	\item Best fit percentage of the manual steering estimated model is 90.27
 \end{itemize}
 \begin{figure}
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
        \caption{Output of Estimated By-Wire System Model}
        \label{fig:byWireSteerModel}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
        \caption{Output of Estimated Manual System Model}
        \label{fig:manualSteerModel}
    \end{minipage}
\end{figure}
  \end{block}
\end{frame}

\begin{frame}{Simulation Results}
  \begin{block}{Acceleration System}
 \begin{itemize}
	\item Best fit percentage of the by-wire acceleration estimated model is 97.69
	\item Best fit percentage of the manual acceleration estimated model is 98.3
 \end{itemize}
 \begin{figure}
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figs/img/byWireAccelArxModel} % first figure itself
        \caption{Output of Estimated By-Wire System Model}
        \label{fig:byWireAccelModel}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figs/img/manualAccelTransferFunctionModel} % second figure itself
        \caption{Output of Estimated Manual System Model}
        \label{fig:manualAccelModel}
    \end{minipage}
\end{figure}
  \end{block}
\end{frame}
